Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of the machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not suitable for side-channel analysis.  Side-channel leakages are a low-level issue and only the low-level analysis can produce the most accurate results. For example, the IR-level branches are not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches with conditional moves, and the converse could also happen. Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.

@@

During the evolution of the computer architecture, researchers found that CPUs process data much faster than the main memory (DRAM) can supply. As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory. By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

>>>>

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of the machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not suitable for side-channel analysis.  Side-channel leakages are a low-level issue and only the low-level analysis can produce the most accurate results. For example, the IR-level branches are not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches with conditional moves, and the converse could also happen. Moreover, translating the machine code into IRs causes a significant overhead for the trace analysis, as we will discuss in the dissertation.

@@

During the evolution of the computer architecture, researchers found that CPUs process data much faster than the main memory (DRAM) can supply. As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPU and the main memory. By caching extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
